Quantum Hoare Type Theory

### 2020-05-25 ms-paper/ms-paper.tex
Add minor feedback from QPL reviewers

\documentclass[acmsmall,nonacm,timestamp]{acmart}

@@

Here, \texttt{rot} takes a qubit and a two-by-two complex-valued unitary matrix (represented as a function from the matrix indices to $\mathbb{C}$) and lets one define arbitrary rotation on a single qubit. \texttt{rot} can then be used to define standard gates such as the hadamard, H, and the Pauli gates, X, Y and Z. \texttt{cond} is the unitary conditional that is used to perform branching unitary operations. For the present paper, we use a simpler conditional, \texttt{ifQ}, that is defined as follows:

@@

\subsubsection{Judgments}
The type system is designed to be bidirectional and syntax directed and hence includes separate judgements for intro and elim terms. We are able to use them unchanged for QHTT.

>>>>

\documentclass[acmsmall,nonacm,timestamp,review=false,anonymous=false]{acmart}

@@

Here, \texttt{rot} takes a qubit and a two-by-two complex-valued unitary matrix (represented as a function from the matrix indices to $\mathbb{C}$) and lets one define arbitrary rotation on a single qubit. \texttt{rot} can then be used to define standard gates such as the Hadamard, H, and the Pauli gates, X, Y and Z. \texttt{cond} is the unitary conditional that is used to perform branching unitary operations. For the present paper, we use a simpler conditional, \texttt{ifQ}, that is defined as follows:

@@

\subsubsection{Judgments}
The type system is designed to be bidirectional and syntax directed and hence it includes separate judgements for intro and elim terms. We are able to use them unchanged for QHTT.
